---
name: "Dr Conor"
surname: "Judge"
position: "Consultant Nephrologist"
address: "11 Garrai De brun, Fort Lorenzo, Galway"
phone: "+353 87 7459259"
profilepic: "conor-judge.jpg"
email: "conorjudge@gmail.com"
twitter: "conorjudge"
linkedin: "conor-judge-44b53121"
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "Input a short bio here. Describe yourself in a couple of sentences."
output: vitae::awesomecv
---

```{r setup, include=FALSE}
orcid_id = "0000-0001-9473-2920"

#tinytex::install_tinytex()

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(vitae)
library(rorcid)
library(dplyr)
library(tidyverse)

```

```{r}
#Beware of Latex and the latex packages needed for compiling. See https://yihui.org/tinytex/r/#debugging if you get any errors related to *.tex compiling 
```

# Education

```{r}

my_ed <- do.call("bind_rows",
  rorcid::orcid_educations("0000-0001-9473-2920")$`0000-0001-9473-2920`$`affiliation-group`$summaries
)

my_ed %>%
  detailed_entries(
    what = `education-summary.role-title`,
    when = glue::glue("{`education-summary.start-date.year.value`} - {`education-summary.end-date.year.value`}"),
    with = `education-summary.organization.name`,
    where = `education-summary.organization.address.city`
  )


```

# Work experience

```{r}
my_exp <- do.call("bind_rows",
  rorcid::orcid_employments("0000-0001-9473-2920")$`0000-0001-9473-2920`$`affiliation-group`$summaries
)

#For the my_exp variable below: if there is no end date on your recent employment, replace `employment-summary.end-date.year.value` with `employment-summary.end-date`. 
my_exp %>%
  detailed_entries(
    what = `employment-summary.role-title`,
    when = glue::glue("{`employment-summary.start-date.year.value`} - {`employment-summary.end-date.year.value`}"),
    with = `employment-summary.organization.name`,
    where = glue::glue("{`employment-summary.organization.address.city`}, {`employment-summary.organization.address.region`}")
  )

```
# Languages:
  
  * **English**: native language.
  * **Spanish**: advanced speaking, writing and reading.
  * **French**: intermediate speaking, writing and reading.

# Skills
These are some of the skills and knowledge I aquired during my training, education and courses

  * **First overarching skillname**:  
      List the details, including software, techniques, etc.
  * **Second overarching skillname**:  
      List the details, including software, techniques, etc.
  * **Other informatic tools**:  
      Microsoft Office; Google Suite; GraphPad Prism; LaTeX; Git; HTML & CSS.
  * **Public speaking**:  
      I  have attended and presented my scientific work in several national and international conferences, both orally and in poster format.
      
# Publications

```{r}

out <- works(orcid_id("0000-0001-9473-2920")) 
 tibble(
   Journal = out$`journal-title.value`,
   Title = out$title.title.value,
   Year = out$`publication-date.year.value`,
   DOI = out$url.value
 ) %>% 
  detailed_entries(
  DOI,
  Journal,
  Title,
  Year
)

```

